UMAP reveals cryptic population structure and phenotype heterogeneity in large genomic cohorts

### 2019-04-10 ms/main.tex
reorient some images

\begin{figure*}
    \centering
    \begin{subfigure}{0.95\textwidth}
    \includegraphics[width=0.95\textwidth]{images/megamontage_eth_ukbb.pdf}
    \end{subfigure}
    \caption{UMAP on UKBB data, colored by self-identified ethnic background. Images are labelled by the number of components included.}
    \label{fig:supp_montage_ukbb_eth}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}{0.95\textwidth}
    \includegraphics[width=0.95\textwidth]{images/montage_ukbb_ns_pm.pdf}
    \end{subfigure}
    \caption{UMAP on UKBB data, colored by northing values, with more blue representing more northern coordinates and more red representing more southern coordinates. Images are labelled by the number of components included. Data has been randomized as explained in the materials and methods section.}
    \label{fig:supp_montage_ukbb_ns}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{images/montage_ukbb_ew_pm.pdf}
    \end{subfigure}
    \caption{UMAP on UKBB data, colored by easting values, with more yellow representing more eastern coordinates and more pink representing more western coordinates. Images are labelled by the number of components included. Data has been randomized as explained in the materials and methods section.}
    \label{fig:supp_montage_ukbb_ew}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}{0.95\textwidth}
    \includegraphics[width=0.95\textwidth]{images/default_clean_size10_alpha60_flip.jpeg}
    \end{subfigure}
    \caption{UMAP on UKBB data, colored by self-identified ethnic background. Images are labelled by the number of components included.}
    \label{fig:supp_montage_ukbb_eth}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}{0.95\textwidth}
    \includegraphics[width=0.95\textwidth]{images/default_clean_size10_alpha60_ns.jpeg}
    \end{subfigure}
    \caption{UMAP on UKBB data, colored by northing values, with more blue representing more northern coordinates and more red representing more southern coordinates. Images are labelled by the number of components included. Data has been randomized as explained in the materials and methods section.}
    \label{fig:supp_montage_ukbb_ns}
\end{figure*}

\begin{figure*}
    \centering
    \begin{subfigure}{\textwidth}
    \includegraphics[width=\textwidth]{images/default_clean_size10_alpha60_ew.jpeg}
    \end{subfigure}
    \caption{UMAP on UKBB data, colored by easting values, with more yellow representing more eastern coordinates and more pink representing more western coordinates. Images are labelled by the number of components included. Data has been randomized as explained in the materials and methods section.}
    \label{fig:supp_montage_ukbb_ew}
\end{figure*}
